---
title: "summary"
author: "Alice Farrelly"
date: "28/03/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

```{r}
print(Sys.time())
```



```{r, include= FALSE, }
hh_all_cntry <- read.csv('././outputs/cleaned_data/1_hh_all_cntry_xsec.csv')
hh_all_cntry_panels <- read.csv('././outputs/cleaned_data/2_hh_all_cntry_panels.csv')
indiv_all_cntry <- read.csv('././outputs/cleaned_data/3_indiv_all_cntry_xsec.csv')
indiv_all_cntry_panels <- read.csv('././outputs/cleaned_data/4_indiv_all_cntry_panels.csv')
hh_summary <- read.csv('././outputs/cleaned_data/5_hh_summary_xsec.csv')
hh_summary_panels <- read.csv('././outputs/cleaned_data/6_hh_summary_panels.csv')
```

# Overview: number of rural households per country per year

### In cross-sectional data
```{r}
# how many rural hh per country per year

rur <- hh_all_cntry %>% filter(relbl_urb_rur == "RURAL")
table(rur$country, rur$year)

```

### Rural households in full panels

```{r}

full_p_rur <- hh_all_cntry_panels %>%
  filter(bp == 1) %>%
  filter(relbl_urb_rur == "RURAL")

table(full_p_rur$country, full_p_rur$year)
```

NER 2018 and ETH 2018 have no households in the panel data set as these are new panels - they are only usable as cross-sectional data. 

# Overview of primary cooking fuel shares for rural households, per country, per year

```{r}
shares <- hh_all_cntry %>%
  filter(relbl_urb_rur == "RURAL") %>%
  group_by(country, year, cooking_fuel_prm_grp) %>% 
  count() %>% # add count of fuel per country per year
  ungroup() %>% 
  group_by(country, year) %>% 
  mutate(ttl = sum(n),# count per year
         pct_ttl = (n / ttl)*100)  # calculate prop of hh using fuel in country per year

print(shares, n = length(shares$country))
```

# Overview of primary cooking fuel shares for rural households, per country, per region, per year

```{r}
shares_rgn <- hh_all_cntry %>%
  filter(relbl_urb_rur == "RURAL") %>%
  group_by(country, relbl_region, year, cooking_fuel_prm_grp) %>% 
  count() %>% # add count of fuel per country per year
  ungroup() %>% 
  group_by(country, relbl_region, year) %>% 
  mutate(ttl = sum(n),# count per year
         pct_ttl = (n / ttl)*100)  # calculate prop of hh using fuel in country per year

print(shares_rgn, n = length(shares_rgn$country))
```

# Balanced panel of original households:Overview of primary cooking fuel shares for rural households, per country, per year

```{r}
shares <- hh_all_cntry_panels %>%
  filter(relbl_urb_rur == "RURAL", bp == 1, orig_hh == 1) %>%
  group_by(country, year, cooking_fuel_prm_grp) %>% 
  count() %>% # add count of fuel per country per year
  ungroup() %>% 
  group_by(country, year) %>% 
  mutate(ttl = sum(n),# count per year
         pct_ttl = (n / ttl)*100)  # calculate prop of hh using fuel in country per year

print(shares, n = length(shares$country))
```


# Balanced panel of original households: Overview of primary cooking fuel shares for rural households, per country, per region, per year

```{r}
shares_rgn <- hh_all_cntry_panels %>%
  filter(relbl_urb_rur == "RURAL", bp == 1, orig_hh == 1) %>%
  group_by(country, relbl_region, year, cooking_fuel_prm_grp) %>% 
  count() %>% # add count of fuel per country per year
  ungroup() %>% 
  group_by(country, relbl_region, year) %>% 
  mutate(ttl = sum(n),# count per year
         pct_ttl = (n / ttl)*100)  # calculate prop of hh using fuel in country per year

print(shares_rgn, n = length(shares_rgn$country))
```



```{r, include = FALSE, echo=FALSE}
# create vector of unique variable names in all dfs of interest
library(dplyr)
all_vars <- unique(c(names(hh_all_cntry), names(hh_all_cntry_panels), names(hh_summary), names(hh_summary_panels), names(indiv_all_cntry), names(indiv_all_cntry_panels)))
#write.csv(all_vars, './lookup/tmp/vars.csv', row.names = FALSE)

# read in edited csv which includes flag for variable type
var_classes <- read.csv('././lookup/vars2.csv')

# For each of the dfs of interest, change character class based on the class column of var_classes$class column #######
# code solution to do this from here: https://stackoverflow.com/questions/65541605/writing-a-custom-function-to-convert-class-of-variables-in-a-dataframe-based-on
hh_all_cntry <- hh_all_cntry %>% 
  mutate(across(any_of(var_classes$var_name), 
                ~get(paste0("as.",var_classes[var_classes$var_name == cur_column(),"class"]))(.x)))

hh_all_cntry_panels <- hh_all_cntry_panels %>% 
  mutate(across(any_of(var_classes$var_name), 
                ~get(paste0("as.",var_classes[var_classes$var_name == cur_column(),"class"]))(.x)))


hh_summary <- hh_summary %>% 
  mutate(across(any_of(var_classes$var_name), 
                ~get(paste0("as.",var_classes[var_classes$var_name == cur_column(),"class"]))(.x)))

hh_summary_panels <- hh_summary_panels %>% 
  mutate(across(any_of(var_classes$var_name), 
                ~get(paste0("as.",var_classes[var_classes$var_name == cur_column(),"class"]))(.x)))

indiv_all_cntry <- indiv_all_cntry %>% 
  mutate(across(any_of(var_classes$var_name), 
                ~get(paste0("as.",var_classes[var_classes$var_name == cur_column(),"class"]))(.x)))


indiv_all_cntry_panels <- indiv_all_cntry_panels %>% 
  mutate(across(any_of(var_classes$var_name), 
                ~get(paste0("as.",var_classes[var_classes$var_name == cur_column(),"class"]))(.x)))


```

# Household df summary by country

```{r}
countries <- unique(hh_all_cntry$country)
S <- list()
for (country in countries){
  S[[country]] <- (summary(hh_all_cntry[hh_all_cntry$country == country,]))
}
print(S)

```

# Houselohd summarized df by country
## data that has been summarized from inidivdual level observations

```{r}
S <- list()
for (country in countries){
  #tmp <- hh_all_cntry[hh_all_cntry$country == country,]
  S[[country]] <- (summary(hh_summary[hh_summary$country == country,]))
}
print(S)

```


# Individual df summary by country
```{r}
S <- list()
for (country in countries){
  #tmp <- hh_all_cntry[hh_all_cntry$country == country,]
  S[[country]] <- (summary(indiv_all_cntry[indiv_all_cntry$country == country,]))
}
print(S)

```

